%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Fraunhofer Portugal AICOS} % Organization
    {Machine Learning Researcher} % Job title
    {Porto, Portugal} % Location
    {Feb. 2023 - Jul. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed federated learning approach with Flower for computer-aided diagnosis of glaucoma using retinal fundus images.}
        \item {Studied the performance impact of different data distributions and data quality on federated learning strategies.}
        \item {Studied various federated learning strategies and evaluated their performance in multiple scenarios.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fraunhofer Portugal AICOS} % Organization
    {Research Grants} % Job title
    {Porto, Portugal} % Location
    {Jul. 2022 - Oct. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Studied methods for glaucoma diagnosis and retinal layer segmentation in OCT-B images.}
        \item {Developed a computer vision approach for retinal layer segmentation in OCT-B images with OpenCV.}
        \item {Developed a deep learning approach for retinal layer segmentation in OCT-B images with PyTorch.}
        \item {Developed a machine learning approach for glaucoma diagnosis in OCT-B images based on features extracted from segmented layers with Scikit-learn.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
